The \dealii Library, Version 9.2

### 2020-05-28 9.2/paper.tex

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
     Bruno Blais,
     Thomas C. Clevenger,
%     Denis Davydov,
    Marc Fehling,
%     Daniel Garcia-Sanchez,
    Alexander V. Grayver,
%     Graham Harper,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Peter Munch,
%     Ross Maguire Kynch,
    Matthias Maier,
%     Jean-Paul Pelteret,
    Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

%
% \author[4]{Jean-Paul~Pelteret}
%
\author[*1]{Bruno~Turcksin}
%
% \author[12]{David Wells}
% \affil[12]{Department of Mathematics, University of North Carolina,
%   Chapel Hill, NC 27516, USA.
%   {\texttt{drwells@email.unc.edu}}}

\renewcommand{\labelitemi}{--}

>>>>

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
     Bruno Blais,
     Thomas C. Clevenger,
%     Denis Davydov,
    Marc Fehling,
%     Daniel Garcia-Sanchez,
    Alexander V. Grayver,
%     Graham Harper,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Peter Munch,
%     Ross Maguire Kynch,
    Matthias Maier,
%     Jean-Paul Pelteret,
    Reza Rastak,
    Bruno Turcksin,
    David Wells
    Zhuoran Wang,
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

%
% \author[4]{Jean-Paul~Pelteret}
%
 \author[14]{Reza Rastak}
 \affil[14]{Department of Civil and Environmental Engineering,
   Stanford University,
   Stanford, CA 94305, USA.
   {\texttt{rastak@stanford.edu}}}

\author[*1]{Bruno~Turcksin}
%
\author[12]{David Wells}
\affil[12]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

\author[14]{Zhuoran Wang}
\affil[14]{Department of Mathematics, Colorado State University, Fort Collins,
          CO 80523-1874, USA.
{\texttt{zhrwang@colostate.edu}}}         
\renewcommand{\labelitemi}{--}
